Hydra Battles in Coq

### 2020-11-17 doc/hydras.tex
minor changes
minor corrections

\label{sect:hardy}
In order to give an idea of the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{Maths!Hardy Hierarchy}

@@

For instance, the following theorem states that, if $\gamma$ is the sum of a limit ordinal $\beta$ and a finite ordinal $n$, and $\beta$ is a fixpoint of
$\phi(\alpha)$, then $\psi(\alpha,\gamma)=\phi_\alpha(\gamma+1)$.

@@

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Main functions and constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina & Math & Description & Page \\ \hline
canon & canon alpha i & $\canonseq{\alpha}{i}$& Canonical sequence & \pageref{Functions:canon}\\
canonS & canonS alpha i & $\canonseq{\alpha}{i+1}$& Helper for canon & \pageref{Functions:canonS}\\
F\_ & F\_ alpha n & $F_\alpha(n)$ & Wainer's \texttt{F} fast growing hierarchy & \pageref{Functions:F-alpha} \\
H\_ & H\_ alpha n & $H_\alpha(n)$ & Hardy's \texttt{H} fast growing hierarchy & \pageref{Functions:H-alpha} \\
iterate & iterate $f$ $n$ $x$ & $f^{(n)}(x)$ & Functional iteration & \pageref{Functions:iterate} \\
L\_ & L\_ alpha k & $L_\alpha(k)$ & final step of a standard path & \pageref{Functions:L-alpha} \\
succ & succ alpha & & Successor & \pageref{Functions:succ-T1}, \pageref{Functions:succ-sch} \dots \\
zero:Ord & & $0$ & The least ordinal (Schütte's model) & \pageref{Constants:zero:Ord} \\

>>>>

\label{sect:hardy}
In order to give an idea of the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{Maths!Hardy hierarchy}

@@

For instance, the following theorem states that, if $\gamma$ is the sum of a limit ordinal $\beta$ and a finite ordinal $n$, and $\beta$ is a fixpoint of
$\phi_\alpha$, then $\psi(\alpha,\gamma)=\phi_\alpha(\gamma+1)$.

@@

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Main functions and constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina & Math & Description & Page \\ \hline
canon & canon alpha i & $\canonseq{\alpha}{i}$& canonical sequence & \pageref{Functions:canon}\\
canonS & canonS alpha i & $\canonseq{\alpha}{i+1}$& helper for canon & \pageref{Functions:canonS}\\
F\_ & F\_ alpha n & $F_\alpha(n)$ & Wainer's \texttt{F} fast growing hierarchy & \pageref{Functions:F-alpha} \\
H\_ & H\_ alpha n & $H_\alpha(n)$ & Hardy's \texttt{H} fast growing hierarchy & \pageref{Functions:H-alpha} \\
iterate & iterate $f$ $n$ $x$ & $f^{(n)}(x)$ & functional iteration & \pageref{Functions:iterate} \\
L\_ & L\_ alpha k & $L_\alpha(k)$ & final step of a standard path & \pageref{Functions:L-alpha} \\
succ & succ alpha & & successor & \pageref{Functions:succ-T1}, \pageref{Functions:succ-sch} \dots \\
zero:Ord & & $0$ & the least ordinal (Schütte's model) & \pageref{Constants:zero:Ord} \\
